\bf Model Visualization Techniques for a Social Network Model

### 2017-08-25 paper.Rnw
add correlation plot for senate models and histogram of ms. Need to add discussion and put them somewhere appropriate.

\hh{XXX we tried to estimate the rate based on the simulations - you could include a histogram of the number of changes for the 1000 simulations in the viz part XXX}
\st{XXX I have the fitted models from the 1000 simulations (see Figure \ref{fig:distests}). Is that what you mean? XXX}

@@

@@

>>>>

\hh{XXX we tried to estimate the rate based on the simulations - you could include a histogram of the number of changes for the 1000 simulations in the viz part XXX}
\st{XXX see line 1257 for plot. where should I put it? }

@@

<<corplotsSenate>>=
senM4est <- read.csv("data/congress/senateM4ests.csv")
senM5est <- read.csv("data/congress/senateM5ests.csv")
names(senM4est) <- c("alpha1", "alpha2", "alpha3", "beta1", "beta2", "beta5")
names(senM5est) <- c("alpha1", "alpha2", "alpha3", "beta1", "beta2", "beta6")
senM4est$Model <- "M4"
senM5est$Model <- "M5"
senM4est$Sim <- 1:nrow(senM4est)
senM5est$Sim <- 1:nrow(senM5est)
senM4est2 <- senM4est %>% gather(parameter, estimate, alpha1:beta5) 
senM5est2 <- senM5est %>% gather(parameter, estimate, alpha1:beta6) 
senM45est <- rbind(senM4est2, senM5est2)
senM45est %>% spread(parameter, estimate)-> senM45est2
ggpairs(senM45est2, columns = 3:9, ggplot2::aes(colour=Model, alpha = .5))
@

@@

# histogram of number of MS in 1000 reps
# sfmsall %>% group_by(rep) %>% summarize(noMs = max(ms)) %>% ggplot() + geom_histogram(aes(x = noMs), binwidth = 5)
